Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
Fix unclosed group
typo

\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.

>>>>

\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.}

\section{deflaker case study}
\begin{table}[]
    \begin{tabular}{|l|l|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664& det checker not found \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  \\ \hline
        &  \\ \hline
        &  \\ \hline
    \end{tabular}
\end{table}
